\RequirePackage{plautopatch}
\RequirePackage[l2tabu, orthodox]{nag}

\documentclass[platex,dvipdfmx]{jlreq}			% for platex
% \documentclass[uplatex,dvipdfmx]{jlreq}		% for uplatex
\usepackage{graphicx}
\usepackage{bxtexlogo}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{hyperref} 
\usepackage{amsfonts}
\usepackage{caption}   % キャプションを調整するパッケージ
\usepackage{physics} % package for making some command easier, such as "\qty", "\dd", "\pdv", "\vb", "\mqty", "\braket"
\usepackage{svg}

\author{齊藤孝太朗}
\date{\today}
\begin{document}

\thispagestyle{empty}

\vspace*{1cm}

\begin{center}
    \huge 修士論文
\end{center}

\vspace{3cm}

\begin{center}
    \LARGE
    オルソパラ転換レートの温度依存性
\end{center}

\vspace{4cm}

\begin{center}
    \Large
    指導教員 吉岡 孝高 准教授
\end{center}

\vspace{3cm}

\begin{center}
    \Large
    令和8年1月提出
\end{center}

\vspace{2cm}

\begin{center}
    \Large
    東京大学工学系研究科物理工学専攻\\
    37-246618 齊藤 孝太朗
\end{center}


\newpage
\begin{abstract}
The yellow 1s excitons in a cuprous oxide \(\mathrm{Cu_2O}\) crystal are split into two distinct states depending on the spin configuration: a triply degenerate orthoexciton state and a singly degenerate paraexciton state. Because 1s paraexciton is pure spin triplet state, paraexcitons interact weakly with the radiative field and thus exhibit long lifetimes. Typically, paraexcitons are generated from optically accessible orthoexcitons via an ortho-to-para conversion process. Owing to their long lifetimes, paraexcitons have attracted attention as a candidate for exciton Bose-Einstein condensation (BEC). To investigate the characteristics of a condensate and the kinetics of orthoexcitons and paraexcitons, it is crucial to analyze the ortho-to-para conversion process, which determines the time scales of paraexciton generation.

In this presentation, we review the temperature dependence of the ortho-to-para conversion rate measured at temperatures ranging from 2 K to 20 K. We also present a conversion model that explains experimental results, based on transverse acoustic (TA) phonon scattering [1]. Furthermore, we present the latest results from our group on measurements of the ortho-to-para conversion rate at sub-Kelvin temperatures and validate the proposed conversion model against the experimental data taken at sub-Kelvin temperatures.
\end{abstract}
\newpage
\tableofcontents
\newpage
本論文で使用する主要な記号およびシンボルは以下の通りである。

\begin{table}[h]
    \centering
    \begin{tabular}{|c|m{8cm}|c|}
        \hline
        記号 & 意味・定義 & 単位 \\ \hline
        \( h \) & プランク定数 & \( \mathrm{J \cdot s} \) \\ \hline
        \( \hbar \) & 剣幕プランク定数 (\( \hbar = \frac{h}{2\pi} \)) & \( \mathrm{J \cdot s} \) \\ \hline
        \( E \) & エネルギー & \( \mathrm{J} \) \\ \hline
        \( \nu \) & 周波数 & \( \mathrm{Hz} \) \\ \hline
        \( \lambda \) & 波長 & \( \mathrm{m} \) \\ \hline
        \( k_B \) & ボルツマン定数 & \( \mathrm{J/K} \) \\ \hline
        \( m \) & 質量 & \( \mathrm{kg} \) \\ \hline
        \vdots & \vdots & \vdots \\ \hline
    \end{tabular}
    \caption{記号一覧}
    \label{tab:symbol_list}
\end{table}
\newpage
\input{chapter1.tex}
\input{chapter2-3.tex}
\input{chapter4.tex}
\input{chapter5.tex}
\input{chapter6.tex}
\input{まとめ}

\appendix
\section{冷却方法}
$^3$He-$^4$He混合液を用いた希釈冷凍機の技術により低温環境においての実験が進められてきた。ヘリウムを使うことで$\text{mK}$までの超低温を定常的に保つことができる。

核断熱消磁を用いると
\begin{table}[htbp]
\centering
\begin{tabular}{l|ccccccccc}
\toprule
& \( E \) & \( 8C_3 \) & \( 6C_2 \) & \( 6C_4 \) & \( 3C'_2 \) & \( 8S_6 \) & \( 6\sigma_h \) & \( 6S_4 \) & \( 3\sigma_d \) \\
\midrule
\( A_{1g} \) & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
\( A_{2g} \) & 1 & 1 & -1 & 1 & -1 & 1 & 1 & 1 & -1 \\
\( E_g \) & 2 & -1 & 0 & 2 & 0 & 2 & -1 & 0 & 2 \\
\( T_{1g} \) & 3 & 0 & -1 & -1 & 1 & 3 & 0 & -1 & -1 \\
\( T_{2g} \) & 3 & 0 & 1 & -1 & -1 & 3 & 0 & -1 & -1 \\
\( A_{1u} \) & 1 & 1 & 1 & 1 & 1 & -1 & -1 & -1 & -1 \\
\( A_{2u} \) & 1 & 1 & -1 & 1 & -1 & -1 & -1 & -1 & 1 \\
\( E_u \) & 2 & -1 & 0 & 2 & 0 & -2 & 1 & 0 & 2 \\
\( T_{1u} \) & 3 & 0 & -1 & -1 & 1 & -3 & 0 & 1 & -1 \\
\( T_{2u} \) & 3 & 0 & 1 & -1 & -1 & -3 & 0 & 1 & 1 \\
\bottomrule
\end{tabular}
\caption{Character Table for the \( O_h \) Point Group}
\label{tab:Oh}
\end{table}


\end{document}
